Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
minor issues
pass on abstract (reconsider last sentence later)

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
$9\%$\comments{($23$ misses)} of the $\numFaults{}$ cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves
the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average). To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

\begin{figure}[h]
	\vspace{-0.3cm}
		\centering
		\includegraphics[width=0.415\textwidth]{figures/performance.pdf}
		\vspace{-0.4cm}
		\caption{Cost of Diagnosis ($\Delta{}C$) per variant}
		\label{fig:diagnosis}
\end{figure}

@@

Table \ref{table:st}
presents the statistics to determine if the observed results are
statistically significant. Shapiro-Wilk tests the null hypothesis that
results are drawn from a normal distribution. The test is perfomed for
all techniques and its variants. With $99\%$ of confidence, the
results tell us that the distributions are not normal. Given that $C$
is not normally distributed, we use Friedman test, a non-parametric
statistical test of hypothesis. The null-hypothesis is that the
ranking results of all techniques and variants are the same. With
$99\%$ confidence, the results show that the distributions are
distinct. To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
  \sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square represents the
statistical significance of the diagnostic accuracy amongst the different techniques, i.e.,
if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different.

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to reassess the effects of combining \ds{} with \sfl{}.  With this
combination, components that are often involved in failing but seldom
in passing test runs could be located and their suspiciousness
reduced. Results show that the \ds{}-\sfl{} combination, coined as
Tandem-SL, improves the diagnostic accuracy up to $73.7\%$
(\avgImprov\ on average). Furthermore, results indicate that the risk
of missing faulty statements, which \ds{}'s key limitation, is not
high---~\ds{} misses faulty statements in $9\%$\comments{($23$
  misses)} of the $\numFaults{}$ cases. To sum, we found that the
\ds{}-\sfl{} combination was practical and effective and encourage new
\sfl{} techniques to be evaluated against that optimization.
\end{abstract}

@@

\begin{figure}[h]
	\vspace{-0.3cm}
		\centering
		\includegraphics[width=0.415\textwidth]{figures/performance.pdf}
		\vspace{-0.4cm}
		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
		\label{fig:diagnosis}
\end{figure}

@@

Table \ref{table:st}
presents the statistics to determine if the observed results are
statistically significant. Shapiro-Wilk tests the null hypothesis that
results are drawn from a normal distribution. The test is perfomed for
all techniques and its variants. With $99\%$ of confidence, the
results tell us that the distributions are not normal. Given that $C$
is not normally distributed, we use Friedman test, a non-parametric
statistical test of hypothesis. The null hypothesis is that the
ranking results of all techniques and variants are the same. With
$99\%$ confidence, the results show that the distributions are
distinct. To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
  \sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square represents the
statistical significance of the diagnostic accuracy amongst the different techniques, i.e.,
if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different.
